---
title: "Using `reflora_occurrence`"
author: "Carlos Calderón & Domingos Cardoso"
format: html
editor: visual
---

# Example of Using \`reflora_occurrence\` Function

In this document, we'll demonstrate how to use the \`reflora_occurrence\` function to retrieve specific taxon records from the REFLORA virtual herbariums.

## Function Overview

The \`reflora_occurrence\` function retrieves occurrence data for specific taxa from the REFLORA database. Below, we'll use the function with different parameters to illustrate its capabilities.

## Example Code

To run the example, ensure that the function and any necessary packages are loaded in your R environment.

```{r, message=FALSE, warning=FALSE}
# Load necessary packages
library(dplyr)
library(stringr)
library(tidyselect)
library(magrittr)
library(devtools)
```

Installing the package remotely fromthe Github repository

```{r, results = "hide", message=FALSE, warning=FALSE}
#installing `refloraR`
devtools::install_github("DBOSlab/refloraR")
library(refloraR)
```

Defining taxa, herbariums and RecordYear spam

```{r, message=FALSE, warning=FALSE}
# Define example taxa, herbaria, and RecordYear
fam_taxa <- c("Fabaceae", "Ochnaceae")
herbaria <- c("ALCB", "HUEFS", "K", "RB")
yearSpam <- c("2011", "2014")
```

Running the \`reflora_occurrence\` function

```{r, message=FALSE, warning=FALSE}
# Run the reflora_occurrence function with example parameters
result_1 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = yearSpam,
  verbose = TRUE,
  save = TRUE,
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(result_1[,1:8]))
```

Trying another example. Exploring the "state" argument

```{r, message=FALSE, warning=FALSE}

# Define example taxa, herbarium, RecordYear, and state
fam_taxa <- c("Fabaceae")
herbaria <- c("RB")
year <- c("2008")
state <- "Alagoas"
```

Running the function

```{r, message=FALSE, warning=FALSE}
# Run the reflora_occurrence function with example parameters
result_2 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = year,
  state = state,
  verbose = TRUE,
  save = TRUE,
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(result_2[,1:8]))

```
