---
title: "Filter REFLORA specimen records"
format: html
---

In this document we'll demonstrate how to use the \`reflora_occurrence\` function, with different parameters, to retrieve specific taxon records from the REFLORA virtual herbariums.

## Function Overview

The \`reflora_occurrence\` function retrieves specific taxon records from the REFLORA herbariums {[https://ipt.jbrj.gov.br/reflora}{REFLORA](https://ipt.jbrj.gov.br/reflora}{REFLORA) , hosted by the Rio de Janeiro Botanical Garden {[https://www.gov.br/jbrj}](https://www.gov.br/jbrj}{Rio).

## Installing and loading dependencies

To run the example, ensure that the function and any necessary packages are loaded in your R environment.

```{r, message=FALSE, warning=FALSE}
# Load necessary packages
library(dplyr)
library(stringr)
library(tidyselect)
library(magrittr)
library(devtools)
```

Installing the package remotely from the Github repository

```{r, results = "hide", message=FALSE, warning=FALSE}
#installing `refloraR`
devtools::install_github("DBOSlab/refloraR")
library(refloraR)
```

## Example 1: Defining taxa and Herbarium

```{r, message=FALSE, warning=FALSE}
# Define taxa
fam_taxa <- c("Fabaceae")
herbaria <- c("ALCB")

```

Running the \`reflora_occurrence\` function. We assume that the dwca files, from the \`reflora_download\`, were already downloaded in the "download_reflora" file.

```{r, message=FALSE, warning=FALSE}
# Run the reflora_occurrence function with example parameters
example_1 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  verbose = TRUE,
  save = TRUE,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_1[,3:8]))
```

The function allows as input a vector with several taxa (families, genera and/or species) and herbariums

```{r, message=FALSE, warning=FALSE}

# Define example taxa and herbariums
fam_taxa <- c("Abarema", "Justicia")
herbaria <- c("ALCB", "HUEFS", "K")
```

Running the function

```{r, message=FALSE, warning=FALSE}
# Run the reflora_occurrence function with example parameters
example_1_1 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_1_1[,3:8]))
```

## Example 2: Defining Record year

```{r, message=FALSE, warning=FALSE}
fam_taxa <- c("Guapira")
herbaria <- c("RB")
year_wanted <- "2011"
```

Running the function

```{r, message=FALSE, warning=FALSE}

# Run the reflora_occurrence function with example parameters
example_2 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = year_wanted,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_2[,3:8]))
```

The function also allows a record year spam

```{r, message=FALSE, warning=FALSE}
fam_taxa <- c("Nyctaginaceae", "Ochnaceae")
herbaria <- c("HUCP", "MUFAL")
years_wanted <- c("2011", "2015")
```

Running the function

```{r, message=FALSE, warning=FALSE}

# Run the reflora_occurrence function with the recordYear spam
example_2_1 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = years_wanted,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_2_1[,3:8]))
```

## Example 3: Defining the Brazilian state

```{r, message=FALSE, warning=FALSE}
fam_taxa <- c("Acanthaceae")
herbaria <- c("RB")
year_wanted <- "2011"
Br_state <- c("Bahia")
```

Running the function

```{r, message=FALSE, warning=FALSE}

# Run the reflora_occurrence function with the Brazilian state
example_3 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = year_wanted,
  state = Br_state,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_3[,3:8]))
```

The function also allows as input the Brazilian states' acronyms and a vector with states

```{r, message=FALSE, warning=FALSE}
fam_taxa <- c("Fabaceae", "Nyctaginaceae")
herbaria <- c("RB", "PEL")
year_wanted <- c("2013", "2018")
Br_acronyms <- c("Bahia", "SP") #BA = Bahia; SP = São Paulo
```

Running 'reflora_occurrence'

```{r, message=FALSE, warning=FALSE}

# Run the reflora_occurrence function with the recordYear spam
example_3_1 <- reflora_occurrence(
  herbarium = herbaria,
  taxon = fam_taxa,
  recordYear = year_wanted,
  state = Br_acronyms,
  path = "download_reflora",
  dir = "reflora_occurrence",
  filename = "reflora_occurrence_search"
)

# Display the result
print(head(example_3_1[,3:8]))

```
